Health Burden (per 100k population) by pathway

### 2022-11-29 results/multi_city/health_impacts/health_pathway_tbls.qmd
Change layout of results and remove unused code

plot_pivottable <- function(data, colname = "level1"){
  data |> filter(!str_detect(cause, "lb|ub")) |>   filter((!is.na(!!rlang::sym(colname)))) |>
    group_by(city, scenario, dose, !!rlang::sym(colname)) |>
    summarise(measure_100k = sum(measure_100k)) |> rpivotTable(
      rows = c("city"),
      cols = c("scenario"),
      aggregatorName = "Sum",
      vals = "measure_100k",
      rendererName = "Horizontal Stacked Bar Chart", 
      subtotals = FALSE,
      height = "100%", 
      overflow = "scroll"
    )
}

# shared_deaths_pathway <- SharedData$new(deaths_pathway |> pivot_longer(cols = -c(select(deaths_pathway, -contains("lev")) |> names())))

@@

<!-- ## Reactable -->
<!-- ```{r} -->

<!-- data <- shared_deaths_pathway -->

<!-- htmltools::browsable( -->
<!--   tagList( -->
<!--     div( -->
<!--       div(tags$label("Filter Type", `for` = "cars-type-filter")), -->
<!--       tags$select( -->
<!--         id = "cars-type-filter", -->
<!--         onchange = "Reactable.setFilter('cars-filter-table', 'level1', this.value)", -->
<!--         tags$option("Level", value = "level1"), -->
<!--         lapply(data$name |> unique() |> as.character(), tags$option) -->
<!--       ) -->
<!--     ), -->

<!--     tags$hr("aria-hidden" = "true"), -->

<!--     data$data() |> filter(!str_detect(cause, "lb|ub")) |> filter(!is.na(level1)) |>  group_by(city, scenario, dose, level1) |> -->
<!--       summarise(measure_100k = sum(measure_100k)) |> rpivotTable( -->
<!--         rows = c("city"), -->
<!--         cols = c("scenario"), -->
<!--         aggregatorName = "Sum", -->
<!--         vals = "measure_100k", -->
<!--         rendererName = "Horizontal Stacked Bar Chart", -->
<!--         subtotals = FALSE, -->
<!--         height = "80%", -->
<!--         overflow = "scroll" -->
<!--       ) -->
<!--   ) -->
<!-- ) -->
<!-- ``` -->

>>>>

plot_pivottable <- function(data, colname = "level1"){
  data |> filter(!str_detect(cause, "lb|ub")) |>   filter((!is.na(!!rlang::sym(colname)))) |>
    group_by(city, scenario, dose, !!rlang::sym(colname)) |>
    summarise(measure_100k = sum(measure_100k)) |> rpivotTable(
      cols = c("city"),
      rows = c("dose","scenario"),
      aggregatorName = "Sum",
      vals = "measure_100k",
      rendererName = "Stacked Bar Chart", 
      inclusions = list(scenario = list("BUS_SC")),
      exclusions= list(city = list("buenos_aires", "santiago")),
      subtotals = FALSE,
      height = "100%", 
      overflow = "scroll"
    )
}

@@
